Review Manuscript

### 2019-04-04 review_article.Rmd
additional author notes included in paper

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

This helps to draw attention to areas, relies of reader being able to see all areas on a map, and know the difference between initial geography and new layout given by a cartogram.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!--
Author notes:
6000 words maximum.
focused  application  of  literature  to address  a  relevant  clinical  issue:
Mapping cancer outcomes
Cartogram applications should point to examples of cancer outcomes, with the main cartogram section discussing sources considered in grey literature review. Examples of political areas may be considered if cancer data is aggregated at these levels.

Future steps should consider applications not currently utilised for cancer outcome displays, where their use may improve decision making
-->

@@

This helps to draw attention to areas, relies on reader being able to see all areas on a map, and know the difference between initial geography and new layout given by a cartogram.
